Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-28 AO_bondedSi.tex
bug fixes to table formatting and reference and labels

\begin{figure}[htbp]
\includegraphics[width=0.4\columnwidth]{figs/VS2021_IR_image.pdf}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tabPatternFills}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are gaps at the interface of the direct bonded Si samples.}
\end{figure}

@@

where $f$ is the areal fill factor of the region exhibiting a finite gap size, and $1-f$ is therefore the areal fill factor of the perfectly bonded area.  $T_e$ is defined in equation \ref{eqn:Tetalon}.  The only free parameters in Equation \ref{eqnMix} are $d$ and $f$.  Both of these parameters are fixed in our direct bonded Si wafers with synthetic gaps, and are listed in Table \ref{tabPatternFills}.  These synthetic imbedded gaps therefore offer an excellent test of our ability to recover the gap axial extent $d$ and areal fill factor $f$ (Section \ref{secKnownGaps}).

@@

\emph{Origin and properties of correlated noise- } Another key assumption of the model is that correlated errors dominate the measurement uncertainty.  This is the same thing as saying that there is an instrumental bias, or that our measurements are \emph{precise} but \emph{inaccurate}.  The extent to which the measurement is inaccurate is tabulated in \ref{tbl_cary5000Pars}, as already mentioned.  We have assumed that the Gaussian Process model can capture the effect of the observed correlated errors.  But to what extent does the Gaussian Process emulate the \emph{True} covariance matrix, which is unknown?  One way to gauge the goodness of fit of the covariance matrix is to generate synthetic data from a best-fit model.  Many of these synthetic draws are shown in the spectra in Figures \rev|\ref{a thru f}| as transparent blue lines.  When overplotted these lines look like a halo of uncertainty enveloping the model and measurement.  The bulk agreement is encouraging.  We also scrutinized individual synthethic spectra with the measured data, and found that the noise model tended to under-predict the length scale of the correlation.  For example, we typically derive $0.15<a<0.4\%$ and $20<s<200$.  The measured data appear to prefer larger values of $s$.  The discrepancy probably comes from the fact that, in reality, the \emph{True} covariance matrix probably has local structures that cannot be replicated by a simple 2-parameter (\emph{i.e.} $a$ and $s$) estimate of the covariance matrix.  A model employing local covariance structures \verb|\cite{Czekala et al. in press}| could better capture some of the residual structure, but would introduce additional computational complexity with little gain.  Overall the Gaussian Process technique provides much better agreement than the na\"{i}ve assumption of zero correlated errors.

\emph{Validating the MCMC with synthetic data, and addressing heteroscedasticity-}  To evaluate our MCMC fitting method and assumption of homoscedasticity, we generated synthetic data with a known parameters, $d$, $f$, $a$, and $s$ and $\sigma_i$.  We then fit the parameters $d$, $f$, $a$, and $s$ assuming homoscedastic errors, ($\sigma_i = \sigma = 0.02\%$).  The derived physical parameters were consistent with the \emph{\Truth} to within the $1\;\sigma$ confidence interval, but we significantly underestimated $s$ (8 nm instead of 200 nm) and marginally underestimated $a$ (0.0013 instead of 0.0016).  This result is reassuring for our estimation of physical parameters, and shows that the Gaussian Process technique captures realistic uncertainty in the physical parameters, despite an imperfect characterization of the noise correlation length.

>>>>

\begin{figure}[htbp]
\includegraphics[width=0.4\columnwidth]{figs/VS2021_IR_image.pdf}
\caption{
\label{figVS2021_IR_image}
IR image of part VS20-21. Three rectangular mesh areas are apparent (Table \ref{tbl_meshPatterns}).  The coarsest mesh, C, shows substructure, while the medium and fine meshes are indistinguishable at the low resolution of the image.  The three dark spots are gaps at the interface of the direct bonded Si samples.}
\end{figure}

@@

where $f$ is the areal fill factor of the region exhibiting a finite gap size, and $1-f$ is therefore the areal fill factor of the perfectly bonded area.  $T_e$ is defined in equation \ref{eqn:Tetalon}.  The only free parameters in Equation \ref{eqnMix} are $d$ and $f$.  Both of these parameters are fixed in our direct bonded Si wafers with synthetic gaps, and are listed in Table \ref{tab_meshPatterns}.  These synthetic imbedded gaps therefore offer an excellent test of our ability to recover the gap axial extent $d$ and areal fill factor $f$ (Section \ref{secKnownGaps}).

@@

\emph{Origin and properties of correlated noise- } Another key assumption of the model is that correlated errors dominate the measurement uncertainty.  This is the same thing as saying that there is an instrumental bias, or that our measurements are \emph{precise} but \emph{inaccurate}.  The extent to which the measurement is inaccurate is tabulated in \ref{tbl_cary5000Pars}, as already mentioned.  We have assumed that the Gaussian Process model can capture the effect of the observed correlated errors.  But to what extent does the Gaussian Process emulate the \emph{True} covariance matrix, which is unknown?  One way to gauge the goodness of fit of the covariance matrix is to generate synthetic data from a best-fit model.  Many of these synthetic draws are shown in the spectra in Figures \verb|\ref{a thru f}| as transparent blue lines.  When overplotted these lines look like a halo of uncertainty enveloping the model and measurement.  The bulk agreement is encouraging.  We also scrutinized individual synthethic spectra with the measured data, and found that the noise model tended to under-predict the length scale of the correlation.  For example, we typically derive $0.15<a<0.4\%$ and $20<s<200$.  The measured data appear to prefer larger values of $s$.  The discrepancy probably comes from the fact that, in reality, the \emph{True} covariance matrix probably has local structures that cannot be replicated by a simple 2-parameter (\emph{i.e.} $a$ and $s$) estimate of the covariance matrix.  A model employing local covariance structures \verb|\cite{Czekala et al. in press}| could better capture some of the residual structure, but would introduce additional computational complexity with little gain.  Overall the Gaussian Process technique provides much better agreement than the na\"{i}ve assumption of zero correlated errors.

\emph{Validating the MCMC with synthetic data, and addressing heteroscedasticity-}  To evaluate our MCMC fitting method and assumption of homoscedasticity, we generated synthetic data with a known parameters, $d$, $f$, $a$, and $s$ and $\sigma_i$.  We then fit the parameters $d$, $f$, $a$, and $s$ assuming homoscedastic errors, ($\sigma_i = \sigma = 0.02\%$).  The derived physical parameters were consistent with the \emph{Truth} to within the $1\;\sigma$ confidence interval, but we significantly underestimated $s$ (8 nm instead of 200 nm) and marginally underestimated $a$ (0.0013 instead of 0.0016).  This result is reassuring for our estimation of physical parameters, and shows that the Gaussian Process technique captures realistic uncertainty in the physical parameters, despite an imperfect characterization of the noise correlation length.
